RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-27 doc/paper.tex
Exp. section: working

The results are displayed in Figure~\ref{fig:compExact_noise_size}. They are grouped with accordance to the (three) formed sub-groups ($x$-axis) and for each of them the exact percentage rate of success of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis). As expected, the success rate is the highest for the small--sized instances; it is sightly bellow 90\% for the clean (no-noise) data. For more noisy data, the success rate of the algorithm gets decreased. For example, on the small-sized instances on the noisy data with the level of noise of 0.01, the rate of success is about 35 \%.

>>>>

The results are displayed in Figure~\ref{fig:compExact_noise_size}. They are grouped with accordance to the (three) formed sub-groups ($x$-axis) and for each of them the exact percentage rate of success of \textsc{Rils}--\textsc{Rols} algorithm is shown ($y$-axis). The following conclusions may be drawn from here:

\begin{itemize}
	\item   As expected, the success rate is the highest for the small--sized instance problems; it is sightly bellow 90\% for the clean (no-noise) data. For more noisy data, the success rate of the algorithm gets decreased. For example, on the small-sized instances with the presence of the noise of level 0.0001, and 0.01, the rate of success of \textsc{Rils}--\textsc{Rols} is still reasonably well, about 55\%~ and 35 \%, respectively. 
	\item For middle-sized instance problems, the rate of success is slightly bellow 50\%. It also decreases by increasing the level of noise in the target data; for the highest level of chosen noise (of 0.01), the success of rate is about 6\%. 
	\item For the large-sized instance problems without the presence of a noise, the rate fo success of \textsc{Rils}--\textsc{Rols} algorithm is at about 25\%, which shows that increase in the size of exact models affects the algorithm's performance, but within reasonable expectations.

	\item We conclude that the size of exact models (solutions) and the increase of the noise level evenly contribute to overall performance of our \textsc{Rils}--\textsc{Rols} method. The success rate of the algorithm (i.e. the exact percentage) seems decreasing linearly  with the average growing size of the exact models, regardless of the value of the noise level.
\end{itemize}
